\resp{COMPAS Star-formation LnL GP surrogate}

### 2024-06-26 src/tex/ms.tex
[showyourwork]
[showyourwork] overleaf sync

\node (start) [startstop] {Sample $\pi(\lambda)$};
\node (compute) [process, below of=start] {Compute $\Lmain$};
\node (train) [process, below of=compute] {Train \Lsurr};
\node (sample) [process, below of=train] {Sample
$p(\lambda|\mathcal{D})\sim\Lsurr\pi(\lambda)$};
\node (check) [decision, below of=sample, yshift=-0.5cm] {\mathcal{O}(\lambda) > N?};

@@

%--------------------------------------------------------
\section{LVK analysis}
\subsection{Data}

@@

>>>>

\node (start) [startstop] {Sample $\pi(\lambda)$};
\node (compute) [process, below of=start] {Compute $\Lmain$};
\node (train) [process, below of=compute] {Train \Lsurr};
\node (sample) [process, below of=train] {Sample 
$p(\lambda|\mathcal{D})\sim\Lsurr\pi(\lambda)$};
\node (check) [decision, below of=sample, yshift=-0.5cm] {$\mathcal{O}(\lambda) > N?$};

@@

%--------------------------------------------------------
\subsection{LVK analysis}
\paragraph{}{Data}

We get the data from the \ogc.
Plots of the event $\Mc,z$ median estimates and $X-\sigma$ uncertainty can be found in Figure X in the Appendix.

@@

\section{OGC4 Events}
